---
title: "Network Comparison"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Network Comparison}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning=FALSE, message=FALSE, fig.width=7, fig.retina = 2, fig.height = 5,
  comment = "#>"
)
```

```{r setup}
library(robber)
library(ggplot2)
library(purrr)
library(tibble)
library(dplyr)
library(stringr)
library(tidyr)
```

We load a collection of all the Seed-Dispersal, Host-Parasite and Plant-Pollinator
of the Web of Life dataset (www.web-of-life.es). All networks have been binarized.
```{r importdatabase}
data("web_of_life", package = "robber")
```

For all these bipartite networks, we will compute the empirical robustness and
the robustness by block model and its variance for uniform extinction sequences.
For example:
```{r 100}
rob_emp <- robustness_emp(web_of_life[[100]]$net)
param <- get_lbm_param(web_of_life[[100]]$net)
rob_bm <- do.call(robustness_lbm, param)
var_rob <- do.call(var_auc_unif_lbm, param)
tb_robustness <- tibble::tibble( 
                    id = web_of_life[[100]]$id,
                    Empirical = rob_emp$auc, 
                    BM = rob_bm$auc, 
                    Variance = var_rob,
                    nr = web_of_life[[100]]$nr,
                    nc = web_of_life[[100]]$nc,
                    dens = web_of_life[[100]]$dens)

print(tb_robustness)
```

And compare the robustness the empirical and Block Model robustness function:
```{r plot100}
ggplot2::ggplot(data.frame(x = seq(0, tb_robustness$nr)/tb_robustness$nr,
                           Empirical = rob_emp$fun,
                           BM = rob_bm$fun),
                ggplot2::aes(x = x, y = Empirical)) +
  ggplot2::geom_step(col = "red") + 
  ggplot2::geom_step(ggplot2::aes(y = BM/BM[1]), linetype = "dashed", col = "blue")
```



We can also compute the robustness by block model for other extinctions sequences:
```{r}
rob_emp_inc <- robustness_emp(web_of_life[[100]]$net, 
                              ext_seq = "increasing")
rob_emp_dec <- robustness_emp(web_of_life[[100]]$net,
                              ext_seq = "decreasing")
rob_bm_inc <- do.call(robustness_lbm, c(param, ext_seq = "increasing"))
rob_bm_dec <- do.call(robustness_lbm, c(param, ext_seq = "decreasing"))
print(c(rob_bm_dec$auc, rob_bm$auc, rob_bm_inc$auc))
```
```{r}
ggplot2::ggplot(data.frame(x = seq(0, tb_robustness$nr)/tb_robustness$nr,
                           Empirical = rob_emp_inc$fun,
                           BM = rob_bm_inc$fun),
                ggplot2::aes(x = x, y = Empirical)) +
  ggplot2::geom_step(col = "red") + 
  ggplot2::geom_step(ggplot2::aes(y = BM/BM[1]), linetype = "dashed", col = "blue")
```
```{r}
par <- list(con = matrix(c(.5, .1),2,1), pi = c(1/3, 2/3), rho = 1, nr = 5, nc = 100)
matrix(flatten_dbl(lapply(seq(50), function(i) {robustness_emp(do.call(simulate_lbm, c(par[1:5]))$A,  ext_seq = "increasing")$fun})), ncol = 6, byrow = TRUE) %>% 
  colMeans() %T>% print() %>% mean()
robustness_lbm(con = matrix(c(.5, .1),2,1), pi = c(1/3, 2/3), rho = 1, nr = 5, nc = 100, ext_seq = "increasing")
```

```{r plot100}
ggplot2::ggplot(data.frame(x = seq(0, tb_robustness$nr)/tb_robustness$nr,
                           Empirical = rob_emp_inc$fun,
                           BM = rob_bm_inc$fun),
                ggplot2::aes(x = x, y = Empirical)) +
  ggplot2::geom_step(col = "red") + 
  ggplot2::geom_step(ggplot2::aes(y = BM/BM[1]), linetype = "dashed", col = "blue")
```

```{r plot100}
ggplot2::ggplot(data.frame(x = seq(0, tb_robustness$nr)/tb_robustness$nr,
                           Empirical = rob_emp_dec$fun,
                           BM = rob_bm_dec$fun),
                ggplot2::aes(x = x, y = Empirical)) +
  ggplot2::geom_step(col = "red") + 
  ggplot2::geom_step(ggplot2::aes(y = BM/BM[1]), linetype = "dashed", col = "blue")
```

```{r}
sum(diff(rob_bm_inc$fun)>0)
diff(rob_bm_inc$fun)>0
param
```
```{r comp_tb_rob_wol}
if (! file.exists("./tb_robustness_wol.rds"))
{
  nb_cores <- parallel::detectCores()/2
  if (is.null(nb_cores)) nb_cores <- 1
  tb_robustness_wol <- pbmcapply::pbmclapply(
    X = seq_along(web_of_life),
    FUN = function(i) {
      if (web_of_life[[i]]$nr > 250) return(NULL)
      rob_emp <- robustness_emp(web_of_life[[i]]$net)$auc
      param <- get_lbm_param(web_of_life[[i]]$net)
      rob_bm <- do.call(robustness_lbm, param)$auc
      rob_bm_inc <- do.call(robustness_lbm, c(param, ext_seq = "increasing"))$auc
      rob_bm_dec <- do.call(robustness_lbm, c(param, ext_seq = "decreasing"))$auc
      bm_blocks <- do.call(robustness_lbm, c(param, ext_seq = "blocks"))
      rob_bm_min <- min(map_dbl(bm_blocks, "auc"))
      rob_bm_max <- max(map_dbl(bm_blocks, "auc"))
      var_rob <- do.call(var_auc_unif_lbm, param)
      tb_tmp <- tibble::tibble(
        id = web_of_life[[i]]$id, 
        Empirical = rob_emp, 
        BM = rob_bm, 
        Variance = var_rob,
        nr = web_of_life[[i]]$nr,
        nc = web_of_life[[i]]$nc,
        dens = web_of_life[[i]]$dens,
        BM_inc = rob_bm_inc,
        BM_dec = rob_bm_dec,
        BM_min = rob_bm_min,
        BM_max = rob_bm_max,
        emp_inc = robustness_emp(web_of_life[[i]]$net, ext_seq = "increasing")$auc,
        emp_dec = robustness_emp(web_of_life[[i]]$net, ext_seq = "decreasing")$auc,
        bm_norm_unif = unlist(compare_robustness(list(param),ext_seq = "uniform")),
        bm_norm_dec = unlist(compare_robustness(list(param),ext_seq = "decreasing")),
        bm_norm_inc = unlist(compare_robustness(list(param),ext_seq = "increasing")),
        K = nrow(param$con),
        Q = ncol(param$con)
      )
      return(tb_tmp)
      # if (stringr::str_sub(web_of_life[[i]]$id, 1, 1) != "M") return(tb_tmp)
      # rob_emp <- robustness_emp(t(web_of_life[[i]]$net))$auc
      # param <- get_lbm_param(t(web_of_life[[i]]$net))
      # rob_bm <- do.call(robustness_lbm, param)$auc
      # rob_bm_inc <- do.call(robustness_lbm, c(param, ext_seq = "increasing"))$auc
      # rob_bm_dec <- do.call(robustness_lbm, c(param, ext_seq = "decreasing"))$auc
      # var_rob <- do.call(var_auc_unif_lbm, param)
      # tb_tmp <- dplyr::bind_rows(
      #   tb_tmp,
      #   tibble::tibble(id = paste(strsplit(web_of_life[[i]]$id, NULL)[[1]][c(1:2,4:3, 5:length(strsplit(web_of_life[[i]]$id, NULL)[[1]]))], collapse=''), 
      #                  Empirical = rob_emp, 
      #                  BM = rob_bm, 
      #                  Variance = var_rob,
      #                  nr = web_of_life[[i]]$nc,
      #                  nc = web_of_life[[i]]$nr,
      #                  dens = web_of_life[[i]]$dens,
      #                  BM_inc = rob_bm_inc,
      #                  BM_dec = rob_bm_dec,
      #                  emp_inc = robustness_emp(t(web_of_life[[i]]$net), ext_seq = "increasing")$auc,
      #                  emp_dec = robustness_emp(t(web_of_life[[i]]$net), ext_seq = "decreasing")$auc))
    }, mc.cores = nb_cores
  )
  tb_robustness_wol <- dplyr::bind_rows(tb_robustness_wol)
  saveRDS(tb_robustness_wol, "./tb_robustness_wol.rds")
} else {
  tb_robustness_wol <- readRDS(file = "./tb_robustness_wol.rds")
}


```
```{r}
#tb_robustness_wol <- bind_rows(map(seq_along(tb_robustness_wol), ~ if(is_tibble(tb_robustness_wol[[.x]])) tb_robustness_wol[[.x]]))
tb_robustness_wol %>% 
  mutate("# Std Deviation" = abs(Empirical - BM)/sqrt(Variance),
         "Empty Column" = (1-dens)**nr) %>% 
  filter(nr >10 & nc >10) %>% 
  filter(! str_sub(id, 3, 4) %in% c("DS", "LP")) %>% 
  group_by(`# Std Deviation`,   
           `Empty Column`) %>% 
  ggplot(aes(y = abs(Empirical - BM)/Empirical,  
             x = `Empty Column`)) +
  geom_point()

```
```{r}
lbm_param <- readRDS("wol_lbm_parameters.rds")
pbiso <- map_dbl(lbm_param, ~ tcrossprod(.x$rho, (1-.x$pi %*% .x$con)^(.x$nr)))
```

```{r}
tb_robustness_wol %>% 
  mutate("# Std Deviation" = abs(Empirical - BM)/sqrt(Variance),
         "Empty Column" = pbiso) %>% 
  dplyr::filter(nr>10 & nc>10) %>% 
  ggplot2::ggplot(ggplot2::aes(x = Empirical, y = BM,#/(1-`Empty Column`), 
                               size = `# Std Deviation`, 
                               col = `Empty Column`)) +
  ggplot2::geom_abline(slope = 1, intercept = 0) + 
  ggplot2::geom_point(alpha = .5) +
  ggplot2::scale_color_gradient( low = "grey50", high = "red") +
  ggplot2::xlim(c(0.5,1)) + 
  ggplot2::ylim(c(0.5,1)) +
  ggplot2::xlab(label = "AUC(R) by Monte Carlo") + 
  ggplot2::ylab(label = "AUC(R) by LBM Expectation") +
  ggplot2::coord_fixed() +
  ggplot2::theme_minimal(base_size = 15, base_rect_size = .25)
#ggsave("wol_goodness_of_fit.png", path = "~/Documents/robustness/robustness/image/",
#       width = 8, height = 6)
#       
```



```{r}
tb_robustness_wol %>% 
  mutate("# Std Deviation" = abs(Empirical - BM)/sqrt(Variance),
         "Empty Column" = pbiso) %>% 
  filter(str_sub(id, 1, 4) == "M_SD") %>% #(1-dens)**nr) %>% 
  dplyr::filter(nr>10 & nc>10) %>% 
  ggplot2::ggplot(ggplot2::aes(x = emp_inc, y = BM_inc,#,/(1-`Empty Column`), 
                               size = `# Std Deviation`, 
                               col = `Empty Column`)) +
  ggplot2::geom_abline(slope = 1, intercept = 0) + 
  ggplot2::geom_point(alpha = .5) +
  ggplot2::scale_color_gradient( low = "grey50", high = "red") +
  ggplot2::xlim(c(0.5,1)) + 
  ggplot2::ylim(c(0.5,1)) +
  ggplot2::xlab(label = "AUC(R) by Monte Carlo") + 
  ggplot2::ylab(label = "AUC(R) by LBM Expectation") +
  ggplot2::coord_fixed() +
  ggplot2::theme_minimal(base_size = 15, base_rect_size = .25)
#ggsave("wol_goodness_of_fit.png", path = "~/Documents/robustness/robustness/image/",
#       width = 8, height = 6)
```
```{r}
tb_robustness_wol %>% 
  mutate("# Std Deviation" = abs(Empirical - BM)/sqrt(Variance),
         "Empty Column" = (1-dens)**nr) %>% 
  dplyr::filter(nr>10 & nc>10) %>% 
  ggplot2::ggplot(ggplot2::aes(x = emp_dec, y = BM_dec, 
                               size = `# Std Deviation`, 
                               col = `Empty Column`)) +
  ggplot2::geom_abline(slope = 1, intercept = 0) + 
  ggplot2::geom_point(alpha = .5) +
  ggplot2::scale_color_gradient( low = "grey50", high = "red") +
  ggplot2::xlim(c(0,1)) + 
  ggplot2::ylim(c(0,1)) +
  ggplot2::xlab(label = "AUC(R) by Monte Carlo") + 
  ggplot2::ylab(label = "AUC(R) by LBM Expectation") +
  ggplot2::coord_fixed() +
  ggplot2::theme_minimal(base_size = 15, base_rect_size = .25)
#ggsave("wol_goodness_of_fit.png", path = "~/Documents/robustness/robustness/image/",
#       width = 8, height = 6)
```

```{r}
tb_robustness_wol %>% 
#  mutate(BM = BM/pbiso, BM_dec = BM_dec/pbiso, BM_inc = BM_inc/pbiso) %>% 
  select(-nr, -nc, -dens, -K, -Q, -Variance) %>% 
  select(where(is.numeric) & ! contains("norm")) %>% 
  cor(use = "pairwise.complete.obs", method = "spearman") 
```

We select the subset of networks where the Robustness by block model has the better
fit on the empirical Robustness:

```{r}
tb_sub <- tb_robustness_wol %>% 
  dplyr::filter((1-dens)**nr <.1 & nr > 10 & nc > 10) %>% 
  dplyr::filter(abs(Empirical - BM)/sqrt(Variance) < 1)
sub_index <- which(tb_robustness_wol$id %in% tb_sub$id)
```

```{r}
tb_sub %>% select(-nr, -nc, -dens, -K, -Q, -Variance) %>% 
  select(where(is.numeric) & ! contains("norm")) %>% 
  cor(use = "pairwise.complete.obs", method = "spearman") 
```

```{r}
if(! file.exists("wol_lbm_fixed.rds")) {
  lbm_par_fixed <- pbmcapply::pbmclapply(
    X = seq_along(web_of_life), 
    FUN = function(i) {
      llll <- NULL
      Q <- c(4, 4)
      while(is.null(llll)) {
        llll <- get_lbm_param(web_of_life[[i]]$net, model_size = Q)
        Q <- Q-1
      }
      llll <- c(llll, QR = length(llll$pi), QC = length(llll$rho))
      return(llll)
    }, mc.cores = 6L)
  saveRDS(lbm_par_fixed, "wol_lbm_fixed.rds")
}
lbm_par_fixed <- readRDS(file = "wol_lbm_fixed.rds")
```
```{r}

ext_seq <- c("uniform", "decreasing", "increasing")
tb_robustness_norm_fixed <-  pbmcapply::pbmclapply(
  X = seq_along(lbm_par_fixed), 
  FUN = function(i) {
    rob <- robustness_lbm(con = do.call(robber:::normalize_lbm_con, c(dens = 0.00156, lbm_par_fixed[[i]][1:5])), 
                                rho = lbm_par_fixed[[i]]$rho,
                                pi = lbm_par_fixed[[i]]$pi, 
                                nr = 1000, 
                                nc = 1000,
                                ext_seq = "blocks")
    
  }, mc.cores = 10L)
tb_robustness_norm_fixed_unif <-  pbmcapply::pbmclapply(
  X = seq_along(lbm_par_fixed), 
  FUN = function(i) {
    rob <- robustness_lbm(con = do.call(robber:::normalize_lbm_con, c(dens = 0.00156, lbm_par_fixed[[i]][1:5])), 
                                rho = lbm_par_fixed[[i]]$rho,
                                pi = lbm_par_fixed[[i]]$pi, 
                                nr = 1000, 
                                nc = 1000,
                                ext_seq = "uniform")
    
  }, mc.cores = 10L)
tb_robustness_norm_fixed_dec <-  pbmcapply::pbmclapply(
  X = seq_along(lbm_par_fixed), 
  FUN = function(i) {
    rob <- robustness_lbm(con = do.call(robber:::normalize_lbm_con, c(dens = 0.00156, lbm_par_fixed[[i]][1:5])), 
                                rho = lbm_par_fixed[[i]]$rho,
                                pi = lbm_par_fixed[[i]]$pi, 
                                nr = 1000, 
                                nc = 1000,
                                ext_seq = "decreasing")
    
  }, mc.cores = 10L)
tb_robustness_norm_fixed_inc <-  pbmcapply::pbmclapply(
  X = seq_along(lbm_par_fixed), 
  FUN = function(i) {
    rob <- robustness_lbm(con = do.call(robber:::normalize_lbm_con, c(dens = 0.00156, lbm_par_fixed[[i]][1:5])), 
                                rho = lbm_par_fixed[[i]]$rho,
                                pi = lbm_par_fixed[[i]]$pi, 
                                nr = 1000, 
                                nc = 1000,
                                ext_seq = "increasing")
    
  }, mc.cores = 10L)
```

```{r}
order(map_dbl(tb_robustness_norm_fixed[[3]], "auc"))
matrix(unlist(map(tb_robustness_norm_fixed[[3]], "block")), ncol = 3, byrow = TRUE)[order(map_dbl(tb_robustness_norm_fixed[[3]], "auc")),]
map_dbl(tb_robustness_norm_fixed[[3]], "auc")
map(tb_robustness_norm_fixed[[3]], "block")
lbm_par_fixed[[3]]

rob_inc <- robustness_lbm(con = do.call(robber:::normalize_lbm_con, c(dens = 0.0156, lbm_par_fixed[[47]][1:5])),
               nr = 100, nc = 100, rho = lbm_par_fixed[[47]]$rho,
                                pi = lbm_par_fixed[[47]]$pi, ext_seq = "increasing" )$auc
 max(map_dbl(tb_robustness_norm_fixed[[3]], "auc"))
matrix(unlist(map(tb_robustness_norm_fixed[[3]], "block")), ncol = 3, byrow = TRUE)[order(map_dbl(tb_robustness_norm_fixed[[3]], "auc")),]
```

```{r}
tb_rob_order <- tibble()
for (i in seq_along(tb_robustness_norm_fixed)) {
  tb_rob_order <- bind_rows(
    tb_rob_order,
    tibble(
      dec_is_min = min(map_dbl(tb_robustness_norm_fixed[[i]], "auc")) == tb_robustness_norm_fixed_dec[[i]]$auc,      
      inc_is_max = max(map_dbl(tb_robustness_norm_fixed[[i]], "auc")) == tb_robustness_norm_fixed_inc[[i]]$auc,
      invmin_is_max = identical(map(tb_robustness_norm_fixed[[i]], "block")[[which.min(map_dbl(tb_robustness_norm_fixed[[i]], "auc"))]],
          rev(map(tb_robustness_norm_fixed[[i]], "block")[[which.max(map_dbl(tb_robustness_norm_fixed[[i]], "auc"))]])),
      rob_min = min(map_dbl(tb_robustness_norm_fixed[[i]], "auc")),
      rob_max = max(map_dbl(tb_robustness_norm_fixed[[i]], "auc"))
    ))
}
tb_rob_order <- tb_rob_order %>% mutate(unif = map_dbl(tb_robustness_norm_fixed_unif, "auc"),
                        dec = map_dbl(tb_robustness_norm_fixed_dec, "auc"),
                        inc = map_dbl(tb_robustness_norm_fixed_inc, "auc"),
                        unif_is_max = unif > rob_max) %>% 
  mutate(id = tb_robustness_wol$id, .before = everything())
colMeans(tb_rob_order[-1])
```

```{r}
tb_rob_order %>% filter(dec_is_min == FALSE | inc_is_max == FALSE | invmin_is_max == FALSE | unif_is_max == TRUE | dec> unif | inc < unif | dec > inc) %>% 
  pivot_longer(where(is.numeric)) %>% 
  ggplot(aes(x = id, y = value, col = name, fill = name, shape = name)) +
           geom_point(size = 3, alpha = .5)
```
```{r}
if (! file.exists("./tb_robustness_wol_fixed.rds"))
{
  nb_cores <- parallel::detectCores()/2
  if( is.null(nb_cores)) nb_cores <- 1
  tb_robustness_wol_fixed <- pbmcapply::pbmclapply(
    X = seq_along(web_of_life),
    FUN = function(i) {
      #      if (web_of_life[[i]]$nr + web_of_life[[i]]$nc > 1000) return(NULL)
      param <- lbm_par_fixed[[i]]
      rob_bm <- do.call(robustness_lbm, param[1:5])$auc
      rob_bm_inc <- do.call(robustness_lbm, c(param[1:5], ext_seq = "increasing"))$auc
      rob_bm_dec <- do.call(robustness_lbm, c(param[1:5], ext_seq = "decreasing"))$auc
      bm_blocks <- do.call(robustness_lbm, c(param[1:5], ext_seq = "blocks"))
      rob_bm_min <- min(map_dbl(bm_blocks, "auc"))
      rob_bm_max <- max(map_dbl(bm_blocks, "auc"))
      tb_tmp <- tibble::tibble(
        id = web_of_life[[i]]$id, 
        BM = rob_bm, 
        nr = web_of_life[[i]]$nr,
        nc = web_of_life[[i]]$nc,
        dens = web_of_life[[i]]$dens,
        BM_inc = rob_bm_inc,
        BM_dec = rob_bm_dec,
        BM_min = rob_bm_min,
        BM_max = rob_bm_max,
        K = nrow(param$con),
        Q = ncol(param$con)
      )
      return(tb_tmp)
      # if (stringr::str_sub(web_of_life[[i]]$id, 1, 1) != "M") return(tb_tmp)
      # rob_emp <- robustness_emp(t(web_of_life[[i]]$net))$auc
      # param <- get_lbm_param(t(web_of_life[[i]]$net))
      # rob_bm <- do.call(robustness_lbm, param)$auc
      # rob_bm_inc <- do.call(robustness_lbm, c(param, ext_seq = "increasing"))$auc
      # rob_bm_dec <- do.call(robustness_lbm, c(param, ext_seq = "decreasing"))$auc
      # var_rob <- do.call(var_auc_unif_lbm, param)
      # tb_tmp <- dplyr::bind_rows(
      #   tb_tmp,
      #   tibble::tibble(id = paste(strsplit(web_of_life[[i]]$id, NULL)[[1]][c(1:2,4:3, 5:length(strsplit(web_of_life[[i]]$id, NULL)[[1]]))], collapse=''), 
      #                  Empirical = rob_emp, 
      #                  BM = rob_bm, 
      #                  Variance = var_rob,
      #                  nr = web_of_life[[i]]$nc,
      #                  nc = web_of_life[[i]]$nr,
      #                  dens = web_of_life[[i]]$dens,
      #                  BM_inc = rob_bm_inc,
      #                  BM_dec = rob_bm_dec,
      #                  emp_inc = robustness_emp(t(web_of_life[[i]]$net), ext_seq = "increasing")$auc,
      #                  emp_dec = robustness_emp(t(web_of_life[[i]]$net), ext_seq = "decreasing")$auc))
    }, mc.cores = nb_cores
  )
  tb_robustness_wol_fixed <- dplyr::bind_rows(tb_robustness_wol_fixed)
  saveRDS(tb_robustness_wol_fixed, "./tb_robustness_wol_fixed.rds")
} else {
  tb_robustness_wol_fixed <- readRDS(file = "./tb_robustness_wol_fixed.rds")
}
```

```{r}
library(magrittr)
tb_robustness_wol_fixed %>% 
  mutate(Empirical = tb_robustness_wol$Empirical,
         emp_dec = tb_robustness_wol$emp_dec,
         emp_inc = tb_robustness_wol$emp_inc) 
  mutate("Empty Column" = (1-dens)**nr) %>% 
  dplyr::filter(nr>10 & nc>10) %>% 
  ggplot2::ggplot(ggplot2::aes(x = emp_inc, y = BM_inc, 
                                      col = `Empty Column`)) +
  ggplot2::geom_abline(slope = 1, intercept = 0) + 
  ggplot2::geom_point(alpha = .5) +
  ggplot2::scale_color_gradient( low = "grey50", high = "red") +
  ggplot2::xlim(c(0.5,1)) + 
  ggplot2::ylim(c(0.5,1)) +
  ggplot2::xlab(label = "AUC(R) by Monte Carlo") + 
  ggplot2::ylab(label = "AUC(R) by LBM Expectation") +
  ggplot2::coord_fixed() +
  ggplot2::theme_minimal(base_size = 15, base_rect_size = .25)

tb_robustness_wol_fixed %>% 
  mutate(Empirical = tb_robustness_wol$Empirical,
         emp_dec = tb_robustness_wol$emp_dec,
         emp_inc = tb_robustness_wol$emp_inc) %>% 
  select(Empirical, BM, emp_dec, BM_dec, emp_inc, BM_inc, BM_min, BM_max) %>% 
  cor(method = "spearman")
  
```
```{r}
indexunif <- with(tb_rob_order, which(( dec> unif | inc < unif | dec > inc)))

map(indexunif, function(i) lbm_par_fixed[[i]])
# Tous ces réseaux ont une structure assortative, très inhabituel. Mais non détecté par l'ICL
tb_robustness_wol[indexunif,] %>% select(id, nr, nc, dens, K, Q,  emp_dec, Empirical, emp_inc)
# 
indexdecmin <- with(tb_rob_order, which(dec_is_min == FALSE ))
indexincmax <- with(tb_rob_order, which((inc_is_max == FALSE )))
indexinv <- with(tb_rob_order, which((invmin_is_max == FALSE )))

map(indexdecmin, function(i) lbm_par_fixed[[i]])
map(indexincmax, function(i) lbm_par_fixed[[i]])

tb_rob_order[indexdecmin,] %>% select(id, rob_min, dec, unif, inc, rob_max)
tb_rob_order[indexincmax,] %>% select(id, rob_min, dec, unif, inc, rob_max)
tb_robustness_wol[indexincmax,] %>% select(id, nr, nc, dens, K, Q,  emp_dec, Empirical, emp_inc)
tb_robustness_wol[indexinv,] %>% select(id, nr, nc, dens, K, Q,  emp_dec, Empirical, emp_inc)

tb_robustness_wol[] %>% 
  filter(id %in% c("M_PL_026", "M_PL_046", "M_PL_072_01", "M_SD_031", "A_HP_031", "A_HP_050", "M_PL_004")) %>% 
  select(id, nr, nc, dens, K, Q,  emp_dec, Empirical, emp_inc)

res <- robustness_lbm(con = do.call(robber:::normalize_lbm_con, c(dens = 0.0156, lbm_par_fixed[[6]][1:5])), 
                                rho = lbm_par_fixed[[6]]$rho,
                                pi = lbm_par_fixed[[6]]$pi, 
                                nr = 100, 
                                nc = 100,
                                ext_seq = "decreasing")
ggplot(tibble(x = seq(0,  100), y = res$fun), aes (x = x, y = y)) +
  geom_line()
```

```{r comp_na_pred}
if (!file.exists("tb_na_pred.rds")) {
  nb_cores <- parallel::detectCores()/2
  if( is.null(nb_cores)) nb_cores <- 1
  tb_na_pred <- pbmcapply::pbmclapply(
    X = seq_along(web_of_life),
    FUN = function(i) {
      # if (! web_of_life[[i]]$id %in% 
      #     c(tb_sub$id,
      #       paste(strsplit(web_of_life[[i]]$id, NULL)[[1]][c(1:2,4:3, 5:length(strsplit(web_of_life[[i]]$id, NULL)[[1]]))], collapse=''))) return(NULL)
      if (! web_of_life[[i]]$id %in% tb_sub$id) return(NULL)
      res <- pbmcapply::pbmclapply(
        X = seq(30),
        FUN = function(iter) {
          A_tmp <- web_of_life[[i]]$net
          trans1 <- sample(seq(3), nrow(A_tmp), replace = TRUE, 
                           prob = c(.50, .25, .25))
          trans2 <- sample(seq(3), ncol(A_tmp), replace = TRUE, 
                           prob = c(.50, .25, .25))
          A_tmp[trans1 == 2, trans2 == 3] <- NA
          A_tmp[trans1 == 3, trans2 == 2] <- NA
          par <- get_lbm_param(A_tmp)    
          return( 
            list(bm_unif = do.call(robustness_lbm, c(par, ext_seq = "uniform"))$auc,
                 bm_dec = do.call(robustness_lbm, c(par, ext_seq = "decreasing"))$auc,
                 bm_inc = do.call(robustness_lbm, c(par, ext_seq = "increasing"))$auc,
                 mc_unif = robustness_emp(A_tmp, ext_seq = "uniform")$auc,
                 mc_dec = robustness_emp(A_tmp, ext_seq = "decreasing")$auc,
                 mc_inc = robustness_emp(A_tmp, ext_seq = "increasing")$auc))      
        })
      rob <-  tb_sub %>% dplyr::filter(id == web_of_life[[i]]$id)
      return(
        tibble::tibble(
          id = rob$id,
          rmse_bm_unif = mean((purrr::map_dbl(res, "bm_unif") - rob$Empirical)**2),
          rmse_bm_dec = mean((purrr::map_dbl(res, "bm_dec") - rob$BM_dec)**2),
          rmse_bm_inc = mean((purrr::map_dbl(res, "bm_inc") - rob$BM_inc)**2),           
          rmse_mc_unif = mean((purrr::map_dbl(res, "mc_unif")- rob$Empirical)**2),
          rmse_mc_dec = mean((purrr::map_dbl(res, "mc_dec") - rob$emp_dec)**2),
          rmse_mc_inc = mean((purrr::map_dbl(res, "mc_inc") - rob$emp_inc)**2),
          mean_bm_unif = mean(purrr::map_dbl(res, "bm_unif")),
          sd_bm_unif = sd(purrr::map_dbl(res, "bm_unif")),
          mean_bm_dec = mean(purrr::map_dbl(res, "bm_dec")),
          sd_bm_dec = sd(purrr::map_dbl(res, "bm_dec")),
          mean_bm_inc = mean(purrr::map_dbl(res, "bm_inc")),
          sd_bm_inc = sd(purrr::map_dbl(res, "bm_inc")),
          mean_mc_unif = mean(purrr::map_dbl(res, "mc_unif")),
          sd_mc_unif = sd(purrr::map_dbl(res, "mc_unif")),
          mean_mc_dec = mean(purrr::map_dbl(res, "mc_dec")),
          sd_mc_dec = sd(purrr::map_dbl(res, "mc_dec")),
          mean_mc_inc = mean(purrr::map_dbl(res, "mc_inc")),
          sd_mc_inc = sd(purrr::map_dbl(res, "mc_inc"))
        )
      )
    }, mc.cores = nb_cores)
  tb_na_pred <- dplyr::bind_rows(tb_na_pred)
  saveRDS(tb_na_pred, file = "tb_na_pred.rds")
} else {
  tb_na_pred <- readRDS(file = "tb_na_pred.rds")
}
```
```{r}
tb_na_pred %>% 
  mutate(Experiment = "Missing Species") %>% 
#  bind_rows(tb_na_pred %>% mutate(Experiment = "NA Interactions")) %>%
  select(starts_with("rmse"), starts_with("Experiment")) %>% 
  pivot_longer(cols = starts_with("rmse"),
               names_to = c("Method", "Extinction"),
               names_sep = 8,
               values_to = "RMSE") %>% 
  mutate(Method = case_when(
    str_sub(Method, 6, 7) == "bm" ~ "Block Model",
    str_sub(Method, 6, 7) == "mc" ~ "Monte Carlo")) %>%
  # mutate(`Extinctions Sequences` = case_when(
  #   Extinction == "inc" ~ "Increasing",
  #   Extinction == "dec" ~ "Decreasing",
  #   Extinction == "unif" ~ "Uniform")) %>%
  mutate(RMSE = sqrt(RMSE)) %>% 
  ggplot(aes(x = Extinction, y = RMSE, fill = Method)) +
  facet_wrap(~ Experiment) +
  geom_boxplot() +
  theme_classic(base_size = 15)
```



<!-- # ```{r} -->
<!-- # tb_na_pred %>%  -->
<!-- #   # purrr::set_names(nm = purrr::flatten_chr(purrr::transpose(web_of_life)$id)) %>%  -->
<!-- #   # tibble::enframe() %>% -->
<!-- #   # dplyr::filter(! is.null(value)) -->
<!-- #   # tidyr::unnest(cols = c(value)) %>%  -->
<!-- #   dplyr::mutate(lbm = purrr::flatten_dbl(purrr::map(value, "bm_unif")), -->
<!-- #          mc = purrr::flatten_dbl(purrr::map(value, "mc_unif"))) %>% -->
<!-- #   pivot_longer(cols = c("lbm", "mc"), names_to = "method", values_to = "rob") %>%  -->
<!-- #   ggplot(aes(x = name, y = rob, fill = method)) + -->
<!-- #   geom_boxplot() + -->
<!-- #   annotate(geom = "segment", y = c(rob_fruit_lbm, rob_pol_lbm), -->
<!-- #            yend = c(rob_fruit_lbm, rob_pol_lbm), -->
<!-- #            x = seq(0, 1)+.5, xend = seq(2)+.5, col = "blue") + -->
<!-- #   annotate(geom = "segment", y = c(rob_fruit_mc, rob_pol_mc),  -->
<!-- #            yend = c(rob_fruit_mc, rob_pol_mc),  -->
<!-- #            x = seq(0, 1)+.5, xend = seq(2)+.5, col = "red")   -->
<!-- # ``` -->


## Applications on networks with missing species

In the next application, we use the same set of networks and assume that only a
fraction of the species were observed (75% on average). 
We also assume that there exists some expert knowledge that brings us 
information about the size of each network and its density (connectance).

```{r comp_missing_spec_pred}
if (!file.exists("tb_missing_species_pred.rds")) {
  nb_cores <- parallel::detectCores()/2
  if( is.null(nb_cores)) nb_cores <- 1
  tb_missing_species_pred <- pbmcapply::pbmclapply(
    X = seq_along(web_of_life),
    FUN = function(i) {
      if (! web_of_life[[i]]$id %in% tb_sub$id) return(NULL)
      res <- pbmcapply::pbmclapply(
        X = seq(30),
        FUN = function(iter) {
          A_tmp <- web_of_life[[i]]$net
          A_tmp <- A_tmp[sample(seq.int(nrow(A_tmp)), round(nrow(A_tmp)*.75)),
                         sample(seq.int(ncol(A_tmp)), round(ncol(A_tmp)*.75))]
          # while(sum(A_tmp) < max(nrow(A_tmp), ncol(A_tmp))) {
          #   A_tmp <- web_of_life[[i]]$net
          #   A_tmp <- A_tmp[sample(seq.int(nrow(A_tmp)), round(nrow(A_tmp)*.75)),
          #                  sample(seq.int(ncol(A_tmp)), round(ncol(A_tmp)*.75))]          
          # }
          par <- get_lbm_param(A_tmp)    
          return( 
            list(
              bm_unif_nonorm = do.call(auc_robustness_lbm, par),
              bm_dec_nonorm = do.call(robustness_lbm, c(par, ext_seq = "decreasing"))$auc,
              bm_inc_nonorm = do.call(robustness_lbm, c(par, ext_seq = "increasing"))$auc,
              bm_unif_size = unlist(compare_robustness(list(par), 
                                                       new_nr = web_of_life[[i]]$nr,
                                                       new_nc = web_of_life[[i]]$nc,
                                                       dens = mean(A_tmp),
                                                       ext_seq = "uniform")),
              bm_dec_size = unlist(compare_robustness(list(par), 
                                                      new_nr = web_of_life[[i]]$nr,
                                                      new_nc = web_of_life[[i]]$nc,
                                                      dens = mean(A_tmp),
                                                      ext_seq = "decreasing")),
              bm_inc_size = unlist(compare_robustness(list(par), 
                                                      new_nr = web_of_life[[i]]$nr,
                                                      new_nc = web_of_life[[i]]$nc,
                                                      dens = mean(A_tmp),
                                                      ext_seq = "increasing")),
              bm_unif = unlist(compare_robustness(list(par), 
                                                  new_nr = web_of_life[[i]]$nr,
                                                  new_nc = web_of_life[[i]]$nc,
                                                  dens = web_of_life[[i]]$dens,
                                                  ext_seq = "uniform")),
              bm_dec = unlist(compare_robustness(list(par), 
                                                 new_nr = web_of_life[[i]]$nr,
                                                 new_nc = web_of_life[[i]]$nc,
                                                 dens = web_of_life[[i]]$dens,
                                                 ext_seq = "decreasing")),
              bm_inc = unlist(compare_robustness(list(par), 
                                                 new_nr = web_of_life[[i]]$nr,
                                                 new_nc = web_of_life[[i]]$nc,
                                                 dens = web_of_life[[i]]$dens,
                                                 ext_seq = "increasing")),
              mc_unif = robustness_emp(A_tmp, ext_seq = "uniform")$auc,
              mc_dec = robustness_emp(A_tmp, ext_seq = "decreasing")$auc,
              mc_inc = robustness_emp(A_tmp, ext_seq = "increasing")$auc))      
        }, mc.cores = nb_cores)
      rob <- tb_sub %>% dplyr::filter(id == web_of_life[[i]]$id)
      return(
        tibble::tibble(
          id = rob$id,
          rmse_bm_unif = mean((purrr::map_dbl(res, "bm_unif") - rob$Empirical)**2),
          rmse_bm_dec = mean((purrr::map_dbl(res, "bm_dec") - rob$BM_dec)**2),
          rmse_bm_inc = mean((purrr::map_dbl(res, "bm_inc") - rob$BM_inc)**2),           
          rmse_mc_unif = mean((purrr::map_dbl(res, "mc_unif")- rob$Empirical)**2),
          rmse_mc_dec = mean((purrr::map_dbl(res, "mc_dec") - rob$emp_dec)**2),
          rmse_mc_inc = mean((purrr::map_dbl(res, "mc_inc") - rob$emp_inc)**2),
          mean_bm_unif = mean(purrr::map_dbl(res, "bm_unif")),
          sd_bm_unif = sd(purrr::map_dbl(res, "bm_unif")),
          mean_bm_dec = mean(purrr::map_dbl(res, "bm_dec")),
          sd_bm_dec = sd(purrr::map_dbl(res, "bm_dec")),
          mean_bm_inc = mean(purrr::map_dbl(res, "bm_inc")),
          sd_bm_inc = sd(purrr::map_dbl(res, "bm_inc")),
          mean_mc_unif = mean(purrr::map_dbl(res, "mc_unif")),
          sd_mc_unif = sd(purrr::map_dbl(res, "mc_unif")),
          mean_mc_dec = mean(purrr::map_dbl(res, "mc_dec")),
          sd_mc_dec = sd(purrr::map_dbl(res, "mc_dec")),
          mean_mc_inc = mean(purrr::map_dbl(res, "mc_inc")),
          sd_mc_inc = sd(purrr::map_dbl(res, "mc_inc")),
          rmse_bm_unif_nonorm = mean((purrr::map_dbl(res, "bm_unif_nonorm") - rob$Empirical)**2),
          rmse_bm_dec_nonorm = mean((purrr::map_dbl(res, "bm_dec_nonorm") - rob$BM_dec)**2),
          rmse_bm_inc_nonorm = mean((purrr::map_dbl(res, "bm_inc_nonorm") - rob$BM_inc)**2),  
          rmse_bm_unif_size = mean((purrr::map_dbl(res, "bm_unif_size") - rob$Empirical)**2),
          rmse_bm_dec_size = mean((purrr::map_dbl(res, "bm_dec_size") - rob$BM_dec)**2),
          rmse_bm_inc_size = mean((purrr::map_dbl(res, "bm_inc_size") - rob$BM_inc)**2)
        )
      )
    }, mc.cores = nb_cores)
  tb_missing_species_pred <- dplyr::bind_rows(tb_missing_species_pred)
  saveRDS(tb_missing_species_pred, file = "tb_missing_species_pred.rds")
} else {
  tb_missing_species_pred <- readRDS(file = "tb_missing_species_pred.rds")
}
```

```{r}
tb_missing_species_pred %>% 
  mutate(Experiment = "Missing Species") %>% 
#  bind_rows(tb_na_pred %>% mutate(Experiment = "NA Interactions")) %>%
  select(starts_with("rmse"), starts_with("Experiment")) %>% 
  pivot_longer(cols = starts_with("rmse"),
               names_to = c("Method", "Extinction"),
               names_sep = 8,
               values_to = "RMSE") %>% 
  mutate(Method = case_when(
    str_sub(Method, 6, 7) == "bm" ~ "Block Model",
    str_sub(Method, 6, 7) == "mc" ~ "Monte Carlo")) %>%
  # mutate(`Extinctions Sequences` = case_when(
  #   Extinction == "inc" ~ "Increasing",
  #   Extinction == "dec" ~ "Decreasing",
  #   Extinction == "unif" ~ "Uniform")) %>%
  mutate(RMSE = sqrt(RMSE)) %>% 
  ggplot(aes(x = Extinction, y = RMSE, fill = Method)) +
  facet_wrap(~ Experiment) +
  geom_boxplot() +
  theme_classic(base_size = 15)
```

```{r}
tb_missing_species_pred %>% 
  mutate(Experiment = "Missing Species") %>% 
  bind_rows(tb_na_pred %>% mutate(Experiment = "NA Interactions")) %>%
  select(starts_with("rmse"), starts_with("Experiment")) %>% 
  pivot_longer(cols = starts_with("rmse"),
               names_to = c("Method", "Extinction"),
               names_sep = 8,
               values_to = "RMSE") %>% 
  mutate(Method = case_when(
    str_sub(Method, 6, 7) == "bm" ~ "Block Model",
    str_sub(Method, 6, 7) == "mc" ~ "Monte Carlo")) %>%
  mutate(`Extinctions Sequences` = case_when(
    Extinction == "inc" ~ "Increasing",
    Extinction == "dec" ~ "Decreasing",
    Extinction == "unif" ~ "Uniform")) %>%
  filter(! is.na(`Extinctions Sequences`)) %>% 
  mutate(RMSE = sqrt(RMSE)) %>% 
  ggplot(aes(x = `Extinctions Sequences`, y = RMSE, fill = Method)) +
  facet_wrap(~ Experiment) +
  geom_boxplot() +
  theme_classic(base_size = 15)
# ggsave(filename = "prediction.png", path = "~/Documents/robustness/robustness/image/",
#        width = 9, height = 6)
```


<!-- ## Comparing network of different size -->


<!-- ```{r} -->
<!-- nodf <- map(.x = seq_along(web_of_life), -->
<!--             .f = function(i) { -->
<!--               if (! web_of_life[[i]]$id %in% tb_sub$id) return(NULL) -->
<!--               bipartite::nested(web_of_life[[i]]$net, method = "NODF2")}) -->
<!-- tb_sub %>%  -->
<!--   mutate(`Interaction type` = str_sub(id, 1, 4)) %>%  -->
<!--   mutate(NODF = unlist(nodf)) %>%  -->
<!--   bind_cols(is_cp) %>%  -->
<!--   # bind_cols(is_cp = is_cp) %>%  -->
<!--   mutate(`Interaction type` = case_when( -->
<!--     `Interaction type` == "A_HP" ~ "Host-Parasite", -->
<!--     `Interaction type` == "M_PL" ~ "Pollination", -->
<!--     `Interaction type` == "M_SD" ~ "Seed Dispersal")) %>%  -->
<!--   filter(Q > 1 & K > 1) %>%  -->
<!--   ggplot(aes(x = bm_norm_unif, y = bm_norm_dec, shape = `Interaction type`,  -->
<!--              col =  `Interaction type`)) + -->
<!--   geom_point(data = tb_sub %>% filter(Q > 1 & K > 1), inherit.aes = FALSE, -->
<!--              aes(x = bm_norm_unif, y = bm_norm_dec), -->
<!--              col = "grey80", size = 3, alpha = .5) + -->
<!--   geom_point(aes(size = bm_norm_inc, alpha = NODF), show.legend = FALSE) + -->
<!--   # geom_text(aes(label = str_sub(id, 5, -1)), col = "black") + -->
<!--   coord_fixed() + -->
<!--   facet_wrap(~ `Interaction type`) + -->
<!--   xlab("AUC(R), Uniform") +  -->
<!--   ylab("AUC(R), Decreasing") + -->
<!--   theme_minimal(base_size = 15, base_rect_size = .25) -->
<!-- #ggsave("wol_robustness_by_type.png", path = "~/Documents/robustness/robustness/image/", -->
<!--        # width = 8, height = 4.5) -->
<!-- ``` -->
<!-- ```{r} -->
<!-- tb_sub %>%  -->
<!--   mutate(`Interaction type` = str_sub(id, 1, 4)) %>%  -->
<!--   mutate(NODF = unlist(nodf)) %>% -->
<!--   bind_cols(is_cp) %>%  -->
<!--   select(bm_norm_unif, bm_norm_dec, bm_norm_inc, NODF, cp) %>%  -->
<!--   cor(method = "pearson") -->
<!-- ``` -->


<!-- Using the same collection of networks, we will compute the robustness for -->
<!-- different model size of LBM: -->

<!-- ```{r} -->
<!-- tb_size <- pbmcapply::pbmclapply( -->
<!--   X = seq_along(web_of_life), -->
<!--   FUN = function(i) { -->
<!--     if (! web_of_life[[i]]$id %in% tb_sub$id) return(NULL) -->
<!--     tb_res <- tibble::tibble() -->
<!--     for(k in seq(2, 4)) { -->
<!--       for(q in seq(2, 4)) { -->
<!--         par <- get_lbm_param(web_of_life[[i]]$net, model_size = c(k, q)) -->
<!--         if(! is.null(par)) { -->
<!--           tb_res <- dplyr::bind_rows( -->
<!--             tb_res, -->
<!--             tibble(tibble( -->
<!--               id = web_of_life[[i]]$id, -->
<!--               K = k, -->
<!--               Q = q, -->
<!--               bm_norm_unif = unlist(compare_robustness(list(par),ext_seq = "uniform")), -->
<!--               bm_norm_dec = unlist(compare_robustness(list(par),ext_seq = "decreasing")), -->
<!--               bm_norm_inc = unlist(compare_robustness(list(par),ext_seq = "increasing")))) -->
<!--           ) -->
<!--         } -->
<!--       } -->
<!--     } -->
<!--     return(tb_res) -->
<!--   }, mc.cores = nb_cores) -->
<!-- deg_seq <- map_dbl(.x = web_of_life, -->
<!--                    .f = function(wol) { -->
<!--                      if (! wol$id %in% tb_sub$id) return(NULL) -->
<!--                      (1-colMeans(wol$net)) - (1-colMeans(wol$net))^(wol$nc+1) / -->
<!--                 colMeans(wol$net) -->
<!--                    }) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- tb_size %>%  -->
<!--   mutate(size = K**2+Q) %>%  -->
<!--   select(size, bm_norm_unif, id) %>%  -->
<!--   pivot_wider(names_from = size, values_from = bm_norm_unif) %>% -->
<!--   select(-id) %>%  -->
<!--   cor( method = "spearman", use = "pairwise.complete.obs") %>%  -->
<!--   min() -->
<!-- tb_size %>%  -->
<!--   mutate(size = K**2+Q) %>%  -->
<!--   select(size, bm_norm_inc, id) %>%  -->
<!--   pivot_wider(names_from = size, values_from = bm_norm_inc) %>% -->
<!--   select(-id) %>%  -->
<!--   cor( method = "spearman", use = "pairwise.complete.obs") %>%  -->
<!--   ggcorrplot::ggcorrplot() -->
<!-- tb_size %>%  -->
<!--   mutate(size = K**2+Q) %>%  -->
<!--   select(size, bm_norm_dec, id) %>%  -->
<!--   pivot_wider(names_from = size, values_from = bm_norm_dec) %>% -->
<!--   select(-id) %>%  -->
<!--   cor( method = "spearman", use = "pairwise.complete.obs") %>%  -->
<!--   ggcorrplot::ggcorrplot() -->

<!-- tb_size %>%  -->
<!--   mutate(size = K**2+Q) %>%  -->
<!--   select(size, bm_norm_unif, id) %>%  -->
<!--   pivot_wider(names_from = size, values_from = bm_norm_unif) %>% -->
<!--   select(-id) %>%  -->
<!--   cor( method = "pearson", use = "pairwise.complete.obs") %>%  -->
<!--   ggcorrplot::ggcorrplot() -->
<!-- tb_size %>%  -->
<!--   mutate(size = K**2+Q) %>%  -->
<!--   select(size, bm_norm_inc, id) %>%  -->
<!--   pivot_wider(names_from = size, values_from = bm_norm_inc) %>% -->
<!--   select(-id) %>%  -->
<!--   cor( method = "pearson", use = "pairwise.complete.obs") %>%  -->
<!--   ggcorrplot::ggcorrplot() -->
<!-- tb_size %>%  -->
<!--   mutate(size = K**2+Q) %>%  -->
<!--   select(size, bm_norm_dec, id) %>%  -->
<!--   pivot_wider(names_from = size, values_from = bm_norm_dec) %>% -->
<!--   select(-id) %>%  -->
<!--   cor( method = "pearson", use = "pairwise.complete.obs") %>%  -->
<!--   ggcorrplot::ggcorrplot()   -->
<!-- ``` -->


<!-- ```{r} -->
<!-- tb_size %>%  -->
<!--   mutate(`Interaction type` = str_sub(id, 1, 4)) %>%  -->
<!--   mutate(`Interaction type` = case_when( -->
<!--     `Interaction type` == "A_HP" ~ "Host-Parasite", -->
<!--     `Interaction type` == "M_PL" ~ "Pollination", -->
<!--     `Interaction type` == "M_SD" ~ "Seed Dispersal")) %>%  -->
<!--   filter(K == 3, Q == 3) %>%  -->
<!--   ggplot(aes(x = bm_norm_unif, y = bm_norm_dec, shape = `Interaction type`,  -->
<!--              col = `Interaction type`)) + -->
<!--   geom_point(data = tb_size %>% filter(K == 3, Q == 3), inherit.aes = FALSE, -->
<!--              aes(x = bm_norm_unif, y = bm_norm_dec), -->
<!--              col = "grey80", size = 3, alpha = .5) + -->
<!--   geom_point(aes(size = bm_norm_inc), show.legend = "none") + -->
<!--   coord_fixed() + -->
<!--   facet_wrap(~ `Interaction type`) + -->
<!--   xlab("AUC(R), Uniform") +  -->
<!--   ylab("AUC(R), Decreasing") + -->
<!--   theme_minimal(base_size = 15) -->
<!-- #ggsave("wol_robustness_by_type.png", path = "~/Documents/robustness/robustness/image/", -->
<!-- #       width = 8, height = 4.5) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- is_cp <- pbmcapply::pbmclapply( -->
<!--   X = seq_along(web_of_life), -->
<!--   FUN = function(i) { -->
<!--     if (! web_of_life[[i]]$id %in% tb_sub$id) return(NULL) -->
<!--     param <- get_lbm_param(web_of_life[[i]]$net, model_size = c(2, 2)) -->
<!--     if(sum(dim(param$con)) != 4) return(FALSE)  -->
<!--     max.cord <-  arrayInd(which.max(param$con), .dim = c(2, 2)) -->
<!--     min.cord <-  arrayInd(which.min(param$con), .dim = c(2, 2)) -->
<!--     delta <- param$con[c(max.cord[,1], setdiff(c(1,2), max.cord[,1])),  -->
<!--                  c(max.cord[,2], setdiff(c(1,2), max.cord[,2]))] -->
<!--     return(tibble(is_cp = (sum(min.cord == max.cord) == 0), -->
<!--                   cp = 1 - .5*(max(delta[1,2], delta[2,1])/delta[1,1] + -->
<!--                                 delta[2,2]/min(delta[1,2], delta[2,1]) ))  -->
<!--     ) -->
<!--   }, mc.cores = nb_cores) -->
<!-- is_cp <- bind_rows(is_cp) -->
<!-- ``` -->



<!-- ## Different sampling effort -->

<!-- ```{r} -->
<!-- tb_missing_realistic <- pbmcapply::pbmclapply( -->
<!--   X = seq_along(web_of_life), -->
<!--   FUN = function(i) { -->
<!--     if (! web_of_life[[i]]$id %in% tb_sub$id) return(NULL) -->
<!--     res <- pbmcapply::pbmclapply( -->
<!--       X = seq(30), -->
<!--       FUN = function(iter) { -->
<!--         A_tmp <- web_of_life[[i]]$net -->
<!--         A_tmp <- A_tmp[sample(seq.int(nrow(A_tmp)), round(nrow(A_tmp)*.75), -->
<!--                               prob = rowSums(A_tmp)),] -->
<!--         A_sub <- A_tmp[rowSums(A_tmp) > 1, ] -->
<!--         while(any(rowSums(A_tmp) != 0)) { -->
<!--           for (i in seq(nrow(A_tmp))) { -->
<!--             if(A_tmp[i,] >1) { -->
<!--               A_tmp[i,] <- 1*(A_tmp[i,] == 1 & ) -->
<!--             } -->
<!--           } -->
<!--           A_tmp[rowSums(A_tmp) > 1, ] <-  1*A_tmp[rowSums(A_tmp) > 1, ]  -->
<!--         } -->
<!--         # while(sum(A_tmp) < max(nrow(A_tmp), ncol(A_tmp))) { -->
<!--         #   A_tmp <- web_of_life[[i]]$net -->
<!--         #   A_tmp <- A_tmp[sample(seq.int(nrow(A_tmp)), round(nrow(A_tmp)*.75)), -->
<!--         #                  sample(seq.int(ncol(A_tmp)), round(ncol(A_tmp)*.75))]           -->
<!--         # } -->
<!--         par <- get_lbm_param(A_tmp)     -->
<!--         return(  -->
<!--           list( -->
<!--             bm_unif_nonorm = do.call(auc_robustness_lbm, par), -->
<!--             bm_dec_nonorm = do.call(robustness_lbm, c(par, ext_seq = "decreasing"))$auc, -->
<!--             bm_inc_nonorm = do.call(robustness_lbm, c(par, ext_seq = "increasing"))$auc, -->
<!--             bm_unif_size = unlist(compare_robustness(list(par),  -->
<!--                                                 new_nr = web_of_life[[i]]$nr, -->
<!--                                                 new_nc = web_of_life[[i]]$nc, -->
<!--                                                 dens = mean(A_tmp), -->
<!--                                                 ext_seq = "uniform")), -->
<!--             bm_dec_size = unlist(compare_robustness(list(par),  -->
<!--                                                new_nr = web_of_life[[i]]$nr, -->
<!--                                                new_nc = web_of_life[[i]]$nc, -->
<!--                                                dens = mean(A_tmp), -->
<!--                                                ext_seq = "decreasing")), -->
<!--             bm_inc_size = unlist(compare_robustness(list(par),  -->
<!--                                                new_nr = web_of_life[[i]]$nr, -->
<!--                                                new_nc = web_of_life[[i]]$nc, -->
<!--                                                dens = mean(A_tmp), -->
<!--                                                ext_seq = "increasing")), -->
<!--             bm_unif = unlist(compare_robustness(list(par),  -->
<!--                                                 new_nr = web_of_life[[i]]$nr, -->
<!--                                                 new_nc = web_of_life[[i]]$nc, -->
<!--                                                 dens = web_of_life[[i]]$dens, -->
<!--                                                 ext_seq = "uniform")), -->
<!--             bm_dec = unlist(compare_robustness(list(par),  -->
<!--                                                new_nr = web_of_life[[i]]$nr, -->
<!--                                                new_nc = web_of_life[[i]]$nc, -->
<!--                                                dens = web_of_life[[i]]$dens, -->
<!--                                                ext_seq = "decreasing")), -->
<!--             bm_inc = unlist(compare_robustness(list(par),  -->
<!--                                                new_nr = web_of_life[[i]]$nr, -->
<!--                                                new_nc = web_of_life[[i]]$nc, -->
<!--                                                dens = web_of_life[[i]]$dens, -->
<!--                                                ext_seq = "increasing")), -->
<!--             mc_unif = robustness_emp(A_tmp, ext_seq = "uniform")$auc, -->
<!--             mc_dec = robustness_emp(A_tmp, ext_seq = "decreasing")$auc, -->
<!--             mc_inc = robustness_emp(A_tmp, ext_seq = "increasing")$auc))       -->
<!--       }, mc.cores = nb_cores) -->
<!--     rob <- tb_sub %>% dplyr::filter(id == web_of_life[[i]]$id) -->
<!--     return( -->
<!--       tibble::tibble( -->
<!--         id = rob$id, -->
<!--         rmse_bm_unif = mean((purrr::map_dbl(res, "bm_unif") - rob$Empirical)**2), -->
<!--         rmse_bm_dec = mean((purrr::map_dbl(res, "bm_dec") - rob$BM_dec)**2), -->
<!--         rmse_bm_inc = mean((purrr::map_dbl(res, "bm_inc") - rob$BM_inc)**2),            -->
<!--         rmse_mc_unif = mean((purrr::map_dbl(res, "mc_unif")- rob$Empirical)**2), -->
<!--         rmse_mc_dec = mean((purrr::map_dbl(res, "mc_dec") - rob$emp_dec)**2), -->
<!--         rmse_mc_inc = mean((purrr::map_dbl(res, "mc_inc") - rob$emp_inc)**2), -->
<!--         mean_bm_unif = mean(purrr::map_dbl(res, "bm_unif")), -->
<!--         sd_bm_unif = sd(purrr::map_dbl(res, "bm_unif")), -->
<!--         mean_bm_dec = mean(purrr::map_dbl(res, "bm_dec")), -->
<!--         sd_bm_dec = sd(purrr::map_dbl(res, "bm_dec")), -->
<!--         mean_bm_inc = mean(purrr::map_dbl(res, "bm_inc")), -->
<!--         sd_bm_inc = sd(purrr::map_dbl(res, "bm_inc")), -->
<!--         mean_mc_unif = mean(purrr::map_dbl(res, "mc_unif")), -->
<!--         sd_mc_unif = sd(purrr::map_dbl(res, "mc_unif")), -->
<!--         mean_mc_dec = mean(purrr::map_dbl(res, "mc_dec")), -->
<!--         sd_mc_dec = sd(purrr::map_dbl(res, "mc_dec")), -->
<!--         mean_mc_inc = mean(purrr::map_dbl(res, "mc_inc")), -->
<!--         sd_mc_inc = sd(purrr::map_dbl(res, "mc_inc")), -->
<!--         rmse_bm_unif_nonorm = mean((purrr::map_dbl(res, "bm_unif_nonorm") - rob$Empirical)**2), -->
<!--         rmse_bm_dec_nonorm = mean((purrr::map_dbl(res, "bm_dec_nonorm") - rob$BM_dec)**2), -->
<!--         rmse_bm_inc_nonorm = mean((purrr::map_dbl(res, "bm_inc_nonorm") - rob$BM_inc)**2),   -->
<!--         rmse_bm_unif_size = mean((purrr::map_dbl(res, "bm_unif_size") - rob$Empirical)**2), -->
<!--         rmse_bm_dec_size = mean((purrr::map_dbl(res, "bm_dec_size") - rob$BM_dec)**2), -->
<!--         rmse_bm_inc_size = mean((purrr::map_dbl(res, "bm_inc_size") - rob$BM_inc)**2) -->
<!--       ) -->
<!--     ) -->
<!--   }, mc.cores = nb_cores) -->
<!-- tb_missing_realistic <- dplyr::bind_rows(tb_missing_realistic) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- tb_missing_species_pred %>%  -->
<!--   mutate(Experiment = "Missing Species") %>%  -->
<!-- #  bind_rows(tb_na_pred %>% mutate(Experiment = "NA Interactions")) %>% -->
<!--   select(starts_with("rmse"), starts_with("Experiment")) %>%  -->
<!--   pivot_longer(cols = starts_with("rmse"), -->
<!--                names_to = c("Method", "Extinction"), -->
<!--                names_sep = 8, -->
<!--                values_to = "RMSE") %>%  -->
<!--   mutate(Method = case_when( -->
<!--     str_sub(Method, 6, 7) == "bm" ~ "Block Model", -->
<!--     str_sub(Method, 6, 7) == "mc" ~ "Monte Carlo")) %>% -->
<!--   # mutate(`Extinctions Sequences` = case_when( -->
<!--   #   Extinction == "inc" ~ "Increasing", -->
<!--   #   Extinction == "dec" ~ "Decreasing", -->
<!--   #   Extinction == "unif" ~ "Uniform")) %>% -->
<!--   mutate(RMSE = sqrt(RMSE)) %>%  -->
<!--   ggplot(aes(x = Extinction, y = RMSE, fill = Method)) + -->
<!--   facet_wrap(~ Experiment) + -->
<!--   geom_boxplot() + -->
<!--   theme_classic(base_size = 15) -->
<!-- ``` -->
