---
title: "Topological Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{topological-analysis}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  fig.width = 6,
  fig.height = 4
)
```

```{r setup}
library(robber)
library(ggplot2)
library(tidyr)
library(dplyr)
library(forcats)
library(purrr)
library(igraph)
theme_set(theme_bw(base_size = 15))
```

In what follows, we will use `robber` to illustrate how different set of
parameters of block models, representing different mesoscale structure
of networks has an influence on the robustness of bipartite ecological
networks. By doing so, we will review the main functions of the package.

# Robustness of real bipartite ecological networks

We load 3 different networks, a host-parasite, a seed-dispersal and a
pollination's one.

```{r}
data("hostparasite", package = "robber")
data("seeddispersal", package = "robber")
data("pollination", package = "robber")
```

They have the following richness and connectance:

```{r}
print(paste0("Host-Parasite: ", nrow(hostparasite), " ", 
           ncol(hostparasite), " ", mean(hostparasite)), sep = ",")
print(paste0("Seed Dispersal: ", nrow(seeddispersal), " ", 
           ncol(seeddispersal), " ", mean(seeddispersal)), sep = ",")
print(paste0("Pollination: ", nrow(pollination), " ", 
           ncol(pollination), " ", mean(pollination)), sep = ",")
```

## Analyzing the robustness of a host-parasite network

To compute the empirical robustness, we can use the function
`robustness_emp()` which uses a Monte Carlo simulation. Several options
are available to choose the type of extinctions sequences and the way
they are computed. The function return a vector of remaining species
after each extinction (\$fun) and the robustness statistic as the area
under the curve (\$auc). For example, using the host-parasite network
and the default uniform extinction sequence:

```{r}
(rob_emp_unif <- robustness_emp(hostparasite))
plot(rob_emp_unif)
```

We can infer a Latent Block Model (LBM) to obtain a sparse parametric
representation of the network by regrouping species into blocks. This
can be done automatically with this package:

```{r}
(lbm_param <- get_lbm_param(hostparasite, ncores = 1L))
```

We can see that the network is divided into 4 blocks (2 groups of hosts
and 2 groups of parasites). The network as a classic core-periphery
structure, with a very connected core ($.95$) composed of about a third
of the species.

Robber compute the robustness as the the robustness function integrated
over all possible networks which arise from the same set of Block Model
parameters.

Given the parameters, we can compute the LBM robustness:

```{r}
(rob_lbm_unif <- do.call(robustness_lbm, lbm_param))
```

As we can see the two robustness statistics are very close:

```{r}
rob_emp_unif$auc
rob_lbm_unif$auc
```

And we can plot the two curves (the empirical one in blue and the LBM
one in black):

```{r}
plot(rob_emp_unif) + 
  plot(rob_lbm_unif, add = TRUE)
```

Using the above parameters we may simulate networks from the same set of
LBM parameters, the black line is the average of all the red dotted line
which are the robustness function of particular realization of networks
issued from the same distribution:

```{r}
rob_fun <- lapply(
  X = seq_len(10),
  FUN = function(i) {
    A <- simulate_lbm(con = lbm_param$con, 
                      pi = lbm_param$pi, 
                      rho = lbm_param$rho, 
                      nr = lbm_param$nr, 
                      nc = lbm_param$nc)$A
    return(list(unif = robustness_emp(A),
           dec = robustness_emp(A, ext_seq = "decreasing"),
           inc = robustness_emp(A, ext_seq = "increasing")))
  }
)
```

```{r}
pu <- plot(rob_emp_unif) + 
  plot(rob_lbm_unif, add = TRUE) +
  plot(rob_fun[[1]]$unif, add = TRUE, lty = "dotted", col = "red") +
  plot(rob_fun[[2]]$unif, add = TRUE, lty = "dotted", col = "red") +
  plot(rob_fun[[3]]$unif, add = TRUE, lty = "dotted", col = "red") +
  plot(rob_fun[[4]]$unif, add = TRUE, lty = "dotted", col = "red") +
  plot(rob_fun[[5]]$unif, add = TRUE, lty = "dotted", col = "red") +
  ggtitle("Uniform")
pu
```

Computing the robustness for other extinctions sequence gives
complementary information on the network. For example extinctions by
decreasing or increasing number of connections may give an information
about a worst-case and best-case scenario.

```{r}
rob_emp_dec <- robustness_emp(hostparasite, ext_seq = "decreasing")
rob_emp_inc <- robustness_emp(hostparasite, ext_seq = "increasing")
rob_emp_dec$auc
rob_emp_inc$auc
```

The above method is very sensitive to the network sampling, in
particular for increasing connection. One way to counter that is to
consider that the order of extinction is a function of the degree, for
example it might depends linearly on it.

```{r}
rob_emp_dec_lin <- robustness_emp(hostparasite, ext_seq = "decreasing", 
                                  method = "linear")
rob_emp_inc_lin <- robustness_emp(hostparasite, ext_seq = "increasing", 
                                  method = "linear")
rob_emp_dec_lin$auc
rob_emp_inc_lin$auc
```

As we can see the obtained robustness values are less extreme and closer
to the one of a uniform primary extinctions distribution.

Using the LBM, we can compute a robustness where the extinction
distribution is dependent of the block memberships of the primary
species. For example, by ordering blocks by their connection
probabilities, and extinguishing species base on this order, we obtain:

```{r}
rob_lbm_dec <- do.call(robustness_lbm, c(lbm_param, ext_seq = "decreasing"))
rob_lbm_inc <- do.call(robustness_lbm, c(lbm_param, ext_seq = "increasing"))
rob_lbm_dec$auc
rob_lbm_inc$auc
```

```{r}
plot(rob_lbm_unif, col = "black", lty = 1) + 
  plot(rob_emp_unif, add = TRUE, col = "blue", lty = 2) +
  plot(rob_emp_dec, add = TRUE, lty = 3, col = "blue") +
  plot(rob_emp_dec_lin, add = TRUE, lty = 4, col = "blue") +
  plot(rob_emp_inc, add = TRUE, lty = 3, col = "blue") +
  plot(rob_emp_inc_lin, add = TRUE, lty = 4, col = "blue") +
  plot(rob_lbm_dec, add = TRUE, lty = 1, col = "black") +
  plot(rob_lbm_inc, add = TRUE, lty = 1, col = "black") +
  ggtitle("Robustness of hostparasite")
```

## Comparing the robustness of 3 networks

How robust is the robustness of the host-parasite network compare to the
one of the pollination and seed dispersal's one? As we have seen above,
the richness and the connectance of these networks are different and it
is difficult to know which part of this difference is due sampling
method and effort. Let first analyze the mesoscale structure of the
mutualistic networks.

```{r}
pl_param <- get_lbm_param(pollination, ncores = 1L)
sd_param <- get_lbm_param(seeddispersal, ncores = 1L)
```

```{r}
pl_param
```

For the pollination network, we have $2$ blocks of plants and $2$ block
of pollinators. About a third of the plants belong to a block which is
equally connected to the whole network. The rest interacts with a high
probability with about a fifth of the pollinators and very rarely with
the rest of the pollinators.

```{r}
sd_param
```

The seed-dispersal networks has a more complex mesoscale structure with
$4$ blocks of plants and $3$ blocks of birds. It has a kind of double
core structure. We compare the three networks using the LBM robustness.

```{r}
pl_lbm_unif <- do.call(robustness_lbm, pl_param)
pl_lbm_dec <- do.call(robustness_lbm, c(pl_param, ext_seq = "decreasing"))
pl_lbm_inc <- do.call(robustness_lbm, c(pl_param, ext_seq = "increasing"))
sd_lbm_unif <- do.call(robustness_lbm, sd_param)
sd_lbm_dec <- do.call(robustness_lbm, c(sd_param, ext_seq = "decreasing"))
sd_lbm_inc <- do.call(robustness_lbm, c(sd_param, ext_seq = "increasing"))
```

```{r echo=FALSE}
df <- data.frame(
  Extinction = c("Uniform", "Increasing", "Decreasing"),
  hostparasite = c(rob_lbm_unif$auc, rob_lbm_inc$auc, rob_lbm_dec$auc),
  pollination = c(pl_lbm_unif$auc, pl_lbm_inc$auc, pl_lbm_dec$auc),
  seeddispersal = c(sd_lbm_unif$auc, sd_lbm_inc$auc, sd_lbm_dec$auc))
knitr::kable(df)
```

As we can see, for all three types of robustness, the seed-dispersal is
more robust than the host-parasite network. The pollination network
being less robust than the other 2. We wish to know which part is due to
the difference in the richness and connectance of these networks and
which part is due there different structure. For this, we will change
the parameters of those networks, using the `compare_robustness()`
function and compute a new robustness, where the difference depends
solely on the mesoscale structure of these networks. For this, we
normalize the networks so they have the connectance of the sparsest
network (`pollination`) and the richness of the richest network
(`seeddispersal` for row species and `pollination` for column species).

```{r}
comp_unif <- compare_robustness(list(lbm_param, pl_param, sd_param), 
                   dens = .148, new_nr = 36, new_nc = 51)
comp_inc <- compare_robustness(list(lbm_param, pl_param, sd_param), 
                   dens = .148, new_nr = 36, new_nc = 51, ext_seq = "increasing")
comp_dec <- compare_robustness(list(lbm_param, pl_param, sd_param), 
                   dens = .148, new_nr = 36, new_nc = 51, ext_seq = "decreasing")
```

```{r echo = FALSE}
dfc <- data.frame(
  Extinction = c("Uniform", "Increasing", "Decreasing"),
  hostparasite = c(comp_unif[[1]], comp_inc[[1]], comp_dec[[1]]),
  pollination = c(comp_unif[[2]], comp_inc[[2]], comp_dec[[2]]),
  seeddispersal = c(comp_unif[[3]], comp_inc[[3]], comp_dec[[3]]))
knitr::kable(dfc)
```

While the robustness of `seeddispersal` is still the highest, we can see
that `pollination` now have a higher robustness than `hostparasite`.
Hence the lack of robustness of `pollination` compared to the other
network was mainly due to its lower connectance and plant richness,
rather than its particular mesoscale structure.

# Comparing the influence of mesoscale structure on robustness

We will compare set of networks that all have the same number of rows,
columns and connectance. We select those numbers such that the upper
bound for the robustness with uniform extinctions is approximately 0.5.

```{r set_constant}
dens <- .0156
nr <-  100
nc <- 100
rob_er <- auc_robustness_lbm(matrix(dens, 1,1), 1, 1, nr, nc)
rob_er
```

```{r echo=FALSE}
mod <- matrix(c("a", 1, 1, "a"), 2, 2)
cp  <- matrix(c("a", "a", "a", 1), 2, 2)
```

We will consider 2 blocks of row species and 2 blocks of column species.
The parameters will be as followed:

-   $\pi$ The row blocks parameter will be set to [1/4, 3/4]

-   $\rho$ The column blocks parameter will vary

-   **con** The connectivity parameters between blocks will be set to
    represent 2 classic topologies:

    -   **Modular** the shape of the connectivity matrix will be as
        follows:

```{r echo=FALSE}
     knitr::kable(mod)
```

-   

    -   **Nested** A classic Core-periphery with or without strong
        connection between the core and the periphery depending on the
        parameters:

```{r echo=FALSE}
     knitr::kable(cp)
```

```{r parameters}
pi <- c(1/4, 3/4)
```

```{r analyse_topo, echo = FALSE}
if (! file.exists("res_topo.rds")) {
  robust_topology <- tibble::tibble()
  eps <- c(1/seq(8, 1.5, by = -.5), seq(1, 8, by = .5))
  for(i in seq(19)) {
    rho <- c(i*.05, (20-i)*.05)
    list_con_mod <- lapply( eps,
                            function(j) {
                              list(con = matrix(c(j, 1,
                                                  1, j), 2, 2),
                                   pi = pi,
                                   rho = rho)})
    rob_mod <- purrr::map_dfc(
      .x = purrr::set_names(c("uniform", "increasing", "decreasing")), 
      .f = function(x) 
        unlist(compare_robustness(list_param = list_con_mod, 
                                  dens = dens, 
                                  new_nr = nr, 
                                  new_nc = nc, 
                                  ext_seq = x))) %>%  
      dplyr::mutate(Topology = "Modular", 
                    rho = rho[1], 
                    j = seq_along(eps))
    list_con_nest <- lapply( eps,
                             function(j) {
                               list(con = matrix(c(j, j,
                                                   j, 1), 2, 2),
                                    pi = pi,
                                    rho = rho)})
    rob_nest <- purrr::map_dfc(.x = purrr::set_names(c("uniform", "increasing", "decreasing")), 
                               .f = function(x) 
                                 unlist(compare_robustness(list_param = list_con_nest, 
                                                           dens = dens, 
                                                           new_nr = nr, 
                                                           new_nc = nc, 
                                                           ext_seq = x))) %>%  
      dplyr::mutate(Topology = "Core-Periphery", 
                    rho = rho[1], 
                    j = seq_along(eps))
    robust_topology <- dplyr::bind_rows(robust_topology, rob_mod, rob_nest)
    saveRDS(robust_topology, "res_topo.rds")
  }
} else {
  robust_topology <- readRDS("res_topo.rds")
}

```

```{r eval=FALSE}
  robust_topology <- tibble::tibble()
  eps <- c(1/seq(8, 1.5, by = -.5), seq(1, 8, by = .5))
  for(i in seq(19)) {
    rho <- c(i*.05, (20-i)*.05)
    list_con_mod <- lapply( eps,
                            function(j) {
                              list(con = matrix(c(j, 1,
                                                  1, j), 2, 2),
                                   pi = pi,
                                   rho = rho)})
    rob_mod <- purrr::map_dfc(
      .x = purrr::set_names(c("uniform", "increasing", "decreasing")), 
      .f = function(x) 
        unlist(compare_robustness(list_param = list_con_mod, 
                                  dens = dens, 
                                  new_nr = nr, 
                                  new_nc = nc, 
                                  ext_seq = x))) %>%  
      dplyr::mutate(Topology = "Modular", 
                    rho = rho[1], 
                    j = seq_along(eps))
    list_con_nest <- lapply( eps,
                             function(j) {
                               list(con = matrix(c(j, j,
                                                   j, 1), 2, 2),
                                    pi = pi,
                                    rho = rho)})
    rob_nest <- purrr::map_dfc(.x = purrr::set_names(c("uniform", "increasing", "decreasing")), 
                               .f = function(x) 
                                 unlist(compare_robustness(list_param = list_con_nest, 
                                                           dens = dens, 
                                                           new_nr = nr, 
                                                           new_nc = nc, 
                                                           ext_seq = x))) %>%  
      dplyr::mutate(Topology = "Core-Periphery", 
                    rho = rho[1], 
                    j = seq_along(eps))
    robust_topology <- dplyr::bind_rows(robust_topology, rob_mod, rob_nest)
  }
```

We print a heatmap going from blue (least robust), to white (same
robustness than a network with no mesoscale structure), to red (more
robust than a network with no structure).

```{r print_topo}
prt <- robust_topology %>%
#  rename(Uniform = uniform, Increasing = increasing, Decreasing = decreasing) +
  tidyr::pivot_longer(cols = c("decreasing","uniform", "increasing"), 
                      names_to = "Extinction", 
                      values_to = "Robustness") %>%
  mutate(Extinction = forcats::as_factor(
    case_when(Extinction == "decreasing" ~ "Decreasing",
              Extinction == "uniform" ~ "Uniform",
              Extinction == "increasing" ~ "Increasing"))) %>% 
  ggplot(ggplot2::aes(x = j, y = rho)) +
  geom_tile(ggplot2::aes(fill = Robustness)) +
  facet_grid(Topology  ~ Extinction) +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                                midpoint = rob_er, 
                                guide_colorbar(title = "R")) +
  annotate(x = 15, y = .5, geom = "point", col = "black", size = 3) +
  annotate(x = 15, y = .55, geom = "text", label = "ER",
                    col = "black", size = 3) +
  scale_x_continuous(breaks = c(0, 7, 15, 22, 30), 
                              labels = c(1/8, 1/4, 1, 4, 8)) +
  coord_fixed(ratio = 30) +
  theme_bw(base_size = 15, base_line_size = 0)

# df_shape <- data.frame(
#   x = c(1, 1, 29, 29, 1, 14),
#   y = c(.05, .05, .05, .5, .95, .05),
#   button = c("a", "d", "b","e", "c", "f"),
#   Topology = rep(c("Core-Periphery", "Modular"), 3),
#   Extinction = c(rep("Decreasing", 2), rep("Increasing", 2), rep("Uniform", 2)))
df_shape <- data.frame(
  x = c(1  , 29 , 29,   29,  1, 1),
  y = c(.85, .05, .35, .95, .6, .4),
  button = c(15L, 17L, 18L, 0L, 2L, 5L),#,
  Topology = rep(c("Core-Periphery", "Modular"), each = 3))
#  Extinction = c(rep("Decreasing", 2), rep("Increasing", 2), rep("Uniform", 2)))
prt + geom_point(data = df_shape, mapping = aes(x = x, y = y, shape = button), 
                 size = 4, show.legend = FALSE)+
  scale_shape_identity() 
```


<!-- ```{r print_topo} -->

<!-- var_er <- var_auc_unif_lbm(matrix(.0156, 1, 1), 1, 1, 100, 100) -->

<!-- prtpres <- robust_topology %>% -->

<!-- #  rename(Uniform = uniform, Increasing = increasing, Decreasing = decreasing) + -->

<!--   tidyr::pivot_longer(cols = c("uniform", "increasing", "decreasing"),  -->

<!--                       names_to = "Extinction",  -->

<!--                       values_to = "Robustness") %>% -->

<!--   mutate(Extinction = as.factor(case_when(Extinction == "uniform" ~ "Uniform", -->

<!--                                 Extinction == "increasing" ~ "Increasing", -->

<!--                                 Extinction == "decreasing" ~ "Decreasing"))) %>%  -->

<!--   filter(Extinction == "Uniform") %>%  -->

<!--   ggplot(ggplot2::aes(x = j, y = rho)) + -->

<!--   geom_tile(ggplot2::aes(fill = Robustness)) + -->

<!--   facet_wrap(~ Topology) + -->

<!--   scale_fill_gradient2(low = "blue", high = "red",  -->

<!--                                 midpoint = rob_er - sqrt(var_er),  -->

<!--                                 guide_colorbar(title = "R")) + -->

<!--   annotate(x = 15, y = .5, geom = "point", col = "black", size = 4) + -->

<!--   annotate(x = 15, y = .55, geom = "text", label = "ER", -->

<!--                     col = "black", size = 3) + -->

<!--   scale_x_continuous(breaks = c(0, 7, 15, 22, 30),  -->

<!--                               labels = c(1/8, 1/4, 1, 4, 8)) + -->

<!--   coord_fixed(ratio = 30) + -->

<!--   theme_bw(base_size = 15, base_line_size = 0) -->

<!-- # df_shape <- data.frame( -->

<!-- #   x = c(1, 1, 29, 29, 1, 14), -->

<!-- #   y = c(.05, .05, .05, .5, .95, .05), -->

<!-- #   button = c("a", "d", "b","e", "c", "f"), -->

<!-- #   Topology = rep(c("Core-Periphery", "Modular"), 3), -->

<!-- #   Extinction = c(rep("Decreasing", 2), rep("Increasing", 2), rep("Uniform", 2))) -->

<!-- df_shape <- data.frame( -->

<!--   x = c(29, 1, 15), -->

<!--   y = c( .35, .75, .05), -->

<!--   button = c(15L, 17L, 18L))#, -->

<!-- #  Topology = rep(c("Core-Periphery", "Modular"), 3), -->

<!-- #  Extinction = c(rep("Decreasing", 2), rep("Increasing", 2), rep("Uniform", 2))) -->

<!-- prtpres + geom_point(data = df_shape, mapping = aes(x = x, y = y, shape = button),  -->

<!--                  size = 5, show.legend = FALSE)+ -->

<!--   scale_shape_identity()  -->

<!-- ``` -->



## Influence of the mesoscale structure on the variability of the robustness

Finally, we will try to figure out how the variability of the robustness
depends on the mesoscale structure of the network and which part of it
comes from the variability in connectance and size of blocks of the
network by restricting ourselves to networks that has the same block
proportions and number of connections between blocks as expected.

We restrict ourselves to 3 classic topologies: ER (no mesoscale
structure), modular (assortative communities) and core-periphery. We
observe that the variability increase with mesoscale structure
complexity and that the main part of it is due to the variance in block
proportions and number of connections between blocks.

```{r compute_gnp}
if (! file.exists("res_gnp.rds")) {
  n_iter <- 300
  pi <- c(.1,.9)
  rho <- c(.2,.8)
  con <- matrix(c(.8, .4, .4, .1), 2, 2)
  con <- 0.1*con/as.vector(pi%*%con%*%rho)
  nr <- 100
  nc <- 100
  res <- pbmcapply::pbmclapply(
    X = seq(500),
    FUN = function(i) {
      G <- simulate_lbm(nr = nr, nc = nc, pi = pi, rho = rho, con = con)
      auc_mc <- robustness_emp(G$A, nb_iter =  n_iter)$auc
      par <- get_lbm_param(G$A)
      auc_lbm <- robustness_lbm(par$con, par$pi, par$rho, nr, nc)$auc
      return(tibble(type = "cp", mc = auc_mc, lbm = auc_lbm ))
    }, mc.cores = 8
  )
  res_cp <- bind_rows(res)
  
  n_iter <- 300
  pi <- 1
  rho <- 1
  con <- matrix(0.1, 1, 1)
  nr <- 100
  nc <- 100
  res <- pbmcapply::pbmclapply(
    X = seq(500),
    FUN = function(i) {
      G <- simulate_lbm(nr = nr, nc = nc, pi = pi, rho = rho, con = con)
      auc_mc <- robustness_emp(G$A, nb_iter =  n_iter)$auc
      par <- get_lbm_param(G$A)
      auc_lbm <- robustness_lbm(par$con, par$pi, par$rho, nr, nc)$auc
      return(tibble(type = "er", mc = auc_mc, lbm = auc_lbm ))
    }, mc.cores = 8
  )
  res_er <- bind_rows(res)
  
  pi  <- c(.2, .8)
  rho <- c(.9, .1)
  con <- matrix(c(.6, .1, .2, .2), 2, 2)
  con <- 0.1*con/as.vector(pi%*%con%*%rho)
  res <- pbmcapply::pbmclapply(
    X = seq(500),
    FUN = function(i) {
      G <- simulate_lbm(nr = nr, nc = nc, pi = pi, rho = rho, con = con)
      auc_mc <- robustness_emp(G$A, nb_iter =  n_iter)$auc
      par <- get_lbm_param(G$A)
      auc_lbm <- robustness_lbm(par$con, par$pi, par$rho, nr, nc)$auc
      return(tibble(type = "mod", mc = auc_mc, lbm = auc_lbm ))
    }, mc.cores = 8
  )
  res_mod <- bind_rows(res)
  res_gnp <- bind_rows(res_cp, res_mod, res_er)
  saveRDS(res_gnp, "res_gnp.rds")
} else {
  res_gnp <- readRDS("res_gnp.rds")
}
```

```{r compute_gnm}
if (! file.exists("res_gnm.rds")) {
  n_iter <- 300
  nr <- 100
  nc <- 100
  
  pi <- c(.1,.9)
  rho <- c(.2,.8)
  con <- matrix(c(.8, .4, .4, .1), 2, 2)
  con <- 0.1*con/as.vector(pi%*%con%*%rho)
  pi <- nr * pi
  rho <- nc * rho
  con <- round(outer(pi, rho) * con)
  
  res <- pbmcapply::pbmclapply(
    X = seq(500),
    FUN = function(i) {
      G <- simulate_lbm(nr = nr, nc = nc, pi = pi, rho = rho, con = con, method = "gnm")
      auc_mc <- robustness_emp(G$A, nb_iter =  n_iter)$auc
      par <- get_lbm_param(G$A)
      auc_lbm <- robustness_lbm(par$con, par$pi, par$rho, nr, nc)$auc
      return(tibble(type = "cp", mc = auc_mc, lbm = auc_lbm ))
    }, mc.cores = 8
  )
  res_cp_gnm <- bind_rows(res)
  
  pi <- 1
  rho <- 1
  con <- matrix(0.1, 1, 1)
  pi <- nr * pi
  rho <- nc * rho
  con <- round(outer(pi, rho) * con)
  res <- pbmcapply::pbmclapply(
    X = seq(500),
    FUN = function(i) {
      G <- simulate_lbm(nr = nr, nc = nc, pi = pi, rho = rho, con = con, method = "gnm")
      auc_mc <- robustness_emp(G$A, nb_iter =  n_iter)$auc
      par <- get_lbm_param(G$A)
      auc_lbm <- robustness_lbm(par$con, par$pi, par$rho, nr, nc)$auc
      return(tibble(type = "er", mc = auc_mc, lbm = auc_lbm ))
    }, mc.cores = 8
  )
  res_er_gnm <- bind_rows(res)
  
  pi  <- c(.2, .8)
  rho <- c(.9, .1)
  con <- matrix(c(.6, .1, .2, .2), 2, 2)
  con <- 0.1*con/as.vector(pi%*%con%*%rho)
  pi <- nr * pi
  rho <- nc * rho
  con <- round(outer(pi, rho) * con)
  res <- pbmcapply::pbmclapply(
    X = seq(500),
    FUN = function(i) {
      G <- simulate_lbm(nr = nr, nc = nc, pi = pi, rho = rho, con = con, method = "gnm")
      auc_mc <- robustness_emp(G$A, nb_iter =  n_iter)$auc
      par <- get_lbm_param(G$A)
      auc_lbm <- robustness_lbm(par$con, par$pi, par$rho, nr, nc)$auc
      return(tibble(type = "mod", mc = auc_mc, lbm = auc_lbm ))
    }, mc.cores = 8
  )
  res_mod_gnm <- bind_rows(res)  
  res_gnm <- bind_rows(res_cp_gnm, res_mod_gnm, res_er_gnm)
  saveRDS(res_gnm, "res_gnm.rds")
} else {
  res_gnm <- readRDS("res_gnm.rds")
}

```

```{r compute_fixed_block}
if (! file.exists("res_block.rds")) {
  n_iter <- 300
  nr <- 100
  nc <- 100
  
  pi <- c(.1,.9)
  rho <- c(.2,.8)
  con <- matrix(c(.8, .4, .4, .1), 2, 2)
  con <- 0.1*con/as.vector(pi%*%con%*%rho)
  simz <- function() {
    A <- diag(0, 100)
     for (k in seq_along(pi)) {
      for (q in seq_along(rho)) {
        A[Z == k, W == q] <- igraph::as_incidence_matrix(
          igraph::sample_bipartite(sum(Z == k), sum(W == q),
                                   type = "gnp", p = con[k,q]))
      }
     }
    return(A)
  }
  
  Z <-  rep(seq(2), times = 100*pi)
  W <-  rep(seq(2), times = 100*rho)
  res <- pbmcapply::pbmclapply(
    X = seq(500),
    FUN = function(i) {
      G <- simz()
      auc_mc <- robustness_emp(G, nb_iter =  n_iter)$auc
      par <- get_lbm_param(G)
      auc_lbm <- robustness_lbm(par$con, par$pi, par$rho, nr, nc)$auc
      return(tibble(type = "cp", mc = auc_mc, lbm = auc_lbm ))
    }, mc.cores = 8
  )
  res_cp_block <- bind_rows(res)
  
  pi <- 1
  rho <- 1
  con <- matrix(0.1, 1, 1)
  Z <-  rep(seq(1), times = 100*pi)
  W <-  rep(seq(1), times = 100*rho)
  res <- pbmcapply::pbmclapply(
    X = seq(500),
    FUN = function(i) {
      G <- simz()
      auc_mc <- robustness_emp(G, nb_iter =  n_iter)$auc
      par <- get_lbm_param(G)
      auc_lbm <- robustness_lbm(par$con, par$pi, par$rho, nr, nc)$auc
      return(tibble(type = "er", mc = auc_mc, lbm = auc_lbm ))
    }, mc.cores = 8
  )
  res_er_block <- bind_rows(res)
  
  pi  <- c(.2, .8)
  rho <- c(.9, .1)
  con <- matrix(c(.6, .1, .2, .2), 2, 2)
  con <- 0.1*con/as.vector(pi%*%con%*%rho)
  W <-  rep(seq(2), times = 100*rho)
  Z <-  rep(seq(2), times = 100*pi)
  res <- pbmcapply::pbmclapply(
    X = seq(500),
    FUN = function(i) {
      G <- simz()
      auc_mc <- robustness_emp(G, nb_iter =  n_iter)$auc
      par <- get_lbm_param(G)
      auc_lbm <- robustness_lbm(par$con, par$pi, par$rho, nr, nc)$auc
      return(tibble(type = "mod", mc = auc_mc, lbm = auc_lbm ))
    }, mc.cores = 8
  )
  res_mod_block <- bind_rows(res)  
  res_block <- bind_rows(res_cp_block, res_mod_block, res_er_block)
  saveRDS(res_block, "res_block.rds")
} else {
  res_block <- readRDS("res_block.rds")
}

```

<!-- ```{r} -->

<!-- res_gnm %>%  -->

<!--   mutate(Model = "Microcanonical") %>%  -->

<!--   bind_rows( -->

<!--       res_gnp %>%  -->

<!--       mutate(Model = "Canonical")) %>%  -->

<!--   bind_rows( -->

<!--     res_block %>%  -->

<!--     mutate(Model = "Fixed Blocks")) %>%  -->

<!--   pivot_longer(cols = - c(type, Model), names_to = "Method", values_to = "Robustness") %>%  -->

<!-- #  rename(Topology = type) %>%  -->

<!--   mutate( -->

<!--     Topology = case_when( -->

<!--       type == "cp" ~ "Core-Periphery", -->

<!--       type == "er" ~ "ER", -->

<!--       type == "mod" ~ "Modular" -->

<!--     )) %>%  -->

<!--   filter(Method == "mc") %>%  -->

<!--   ggplot(aes(x = Robustness, fill = Topology, lty = Topology)) + -->

<!--   ggridges::geom_density_ridges(aes(y = Model), alpha = .3) + -->

<!-- #  geom_density(alpha = .2) + -->

<!--   ylab(label = "") + -->

<!-- #  facet_wrap(~ Model) + -->

<!--   theme_minimal(base_size = 15)  -->

<!-- ``` -->

<!-- ```{r compute_gnp} -->

<!-- if (! file.exists("res_gnp_pres.rds")) { -->

<!--   n_iter <- 300 -->

<!--   pi <- c(.25,.75) -->

<!--   rho <- c(.35,.65) -->

<!--   con <- matrix(c(.8, .8, .8, .1), 2, 2) -->

<!--   con <- 0.0156*con/as.vector(pi%*%con%*%rho) -->

<!--   nr <- 100 -->

<!--   nc <- 100 -->

<!--   res <- pbmcapply::pbmclapply( -->

<!--     X = seq(500), -->

<!--     FUN = function(i) { -->

<!--       G <- simulate_lbm(nr = nr, nc = nc, pi = pi, rho = rho, con = con) -->

<!--       auc_mc <- robustness_emp(G$A, nb_iter =  n_iter)$auc -->

<!--       par <- get_lbm_param(G$A) -->

<!--       auc_lbm <- robustness_lbm(par$con, par$pi, par$rho, nr, nc)$auc -->

<!--       return(tibble(type = "cp", mc = auc_mc, lbm = auc_lbm )) -->

<!--     }, mc.cores = 8 -->

<!--   ) -->

<!--   res_cp <- bind_rows(res) -->

<!--   n_iter <- 300 -->

<!--   pi <- 1 -->

<!--   rho <- 1 -->

<!--   con <- matrix(0.0156, 1, 1) -->

<!--   nr <- 100 -->

<!--   nc <- 100 -->

<!--   res <- pbmcapply::pbmclapply( -->

<!--     X = seq(500), -->

<!--     FUN = function(i) { -->

<!--       G <- simulate_lbm(nr = nr, nc = nc, pi = pi, rho = rho, con = con) -->

<!--       auc_mc <- robustness_emp(G$A, nb_iter =  n_iter)$auc -->

<!--       par <- get_lbm_param(G$A) -->

<!--       auc_lbm <- robustness_lbm(par$con, par$pi, par$rho, nr, nc)$auc -->

<!--       return(tibble(type = "er", mc = auc_mc, lbm = auc_lbm )) -->

<!--     }, mc.cores = 8 -->

<!--   ) -->

<!--   res_er <- bind_rows(res) -->

<!--   pi  <- c(.25, .75) -->

<!--   rho <- c(.35, .65) -->

<!--   con <- matrix(c(.8, .1, .1, .8), 2, 2) -->

<!--   con <- 0.0156*con/as.vector(pi%*%con%*%rho) -->

<!--   res <- pbmcapply::pbmclapply( -->

<!--     X = seq(500), -->

<!--     FUN = function(i) { -->

<!--       G <- simulate_lbm(nr = nr, nc = nc, pi = pi, rho = rho, con = con) -->

<!--       auc_mc <- robustness_emp(G$A, nb_iter =  n_iter)$auc -->

<!--       par <- get_lbm_param(G$A) -->

<!--       auc_lbm <- robustness_lbm(par$con, par$pi, par$rho, nr, nc)$auc -->

<!--       return(tibble(type = "mod", mc = auc_mc, lbm = auc_lbm )) -->

<!--     }, mc.cores = 8 -->

<!--   ) -->

<!--   res_mod <- bind_rows(res) -->

<!--   res_gnp_pres <- bind_rows(res_cp, res_mod, res_er) -->

<!--   saveRDS(res_gnp, "res_gnp_pres.rds") -->

<!-- } else { -->

<!--   res_gnp_pres <- readRDS("res_gnp_pres.rds") -->

<!-- } -->

<!-- ``` -->

```{r}
res_gnp %>% 
  mutate(Model = "Canonical") %>%  
  pivot_longer(cols = - c(type, Model), names_to = "Method", values_to = "Robustness") %>% 
#  rename(Topology = type) %>% 
  mutate(
    Topology = case_when(
      type == "cp" ~ "Core-Periphery",
      type == "er" ~ "ER",
      type == "mod" ~ "Modular"
    )) %>% 
  filter(Method == "mc") %>% 
  ggplot(aes(x = Robustness, fill = Topology, lty = Topology)) +
  geom_density(alpha = .3) +
#  ggridges::geom_density_ridges(aes(y = Model), alpha = .3) +
#  geom_density(alpha = .2) +
  ylab(label = "") +
#  facet_wrap(~ Model) +
  theme_minimal(base_size = 15) 
```
