---
title: "Topological Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Topological Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(robber)
```

In what follows, we will use \code{robber} to illustrate how different 
set of parameters of block models, representing differents topologies of 
network has an influence on the robustness of bipartite ecological networks.

We will compare set of networks that all have the same number of rows,
columns and density. We select those numbers such that the maximum number for
the robustness with uniform extinctions is approximately 0.5.

```{r set_constant}
dens <- .0156
nr <-  100
nc <- 100
rob_er <- auc_robustness_lbm(matrix(dens, 1,1), 1, 1, nr, nc)
rob_er
```

```{r echo=FALSE}
mod <- matrix(c("a", 1, 1, "a"), 2, 2)
cp  <- matrix(c("a", "a", "a", 1), 2, 2)
```

We will consider 2 blocks of row species and 2 blocks of column species. 
The parameters will be as followed:

* $\pi$ The row blocks parameter will be set to [1/4, 3/4]
    
* $\rho$ The column blocks parameter will vary
    
* **con** The connectivity parameters between blocks will be set to 
    represent 2 classic topologies: 
    
    + __Modular__ the shape of the connectivity matrix will be as follows:
   
```{r echo=FALSE}
     knitr::kable(mod)
```

*     
    + __Nested__ A classic Core-periphery with or without strong connection
        between the core and the periphery depending on the parameters:

```{r echo=FALSE}
     knitr::kable(cp)
``` 

```{r parameters}
pi <- c(1/4, 3/4)
```


```{r analyse_artice}
robust_topology <- tibble::tibble()
eps <- c(1/seq(8, 1.5, by = -.5), seq(1, 8, by = .5))
for(i in seq(19)) {
  rho <- c(i*.05, (20-i)*.05)
  list_con_mod <- lapply( eps,
                          function(j) {
                            list(con = matrix(c(j, 1,
                                                1, j), 2, 2),
                                 pi = pi,
                                 rho = rho)})
  rob_mod <- purrr::map_dfc(
    .x = purrr::set_names(c("uniform", "increasing", "decreasing")), 
    .f = function(x) 
      unlist(compare_robustness(list_param = list_con_mod, 
                                dens = dens, 
                                new_nr = nr, 
                                new_nc = nc, 
                                ext_seq = x))) %>%  
    dplyr::mutate(Topology = "Modular", 
                  rho = rho[1], 
                  j = seq_along(eps))
  list_con_nest <- lapply( eps,
                           function(j) {
                             list(con = matrix(c(j, j,
                                                 j, 1), 2, 2),
                                  pi = pi,
                                  rho = rho)})
  rob_nest <- purrr::map_dfc(.x = purrr::set_names(c("uniform", "increasing", "decreasing")), 
                             .f = function(x) 
                               unlist(compare_robustness(list_param = list_con_mod, 
                                                         dens = dens, 
                                                         new_nr = nr, 
                                                         new_nc = nc, 
                                                         ext_seq = x))) %>%  
    dplyr::mutate(Topology = "Nested", 
                  rho = rho[1], 
                  j = seq_along(eps))
  robust_topology <- dplyr::bind_rows(robust_topology, rob_mod, rob_nest)
}
```



```{r print_article}
robust_topology %>%
  tidyr::pivot_longer(cols = c("uniform", "increasing", "decreasing"), 
                      names_to = "Extinction", 
                      values_to = "Robustness") %>%
  ggplot2::ggplot(ggplot2::aes(x = j, y = rho)) +
  ggplot2::geom_tile(ggplot2::aes(fill = Robustness)) +
  ggplot2::facet_grid(Topology  ~ Extinction) +
  ggplot2::scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                                midpoint = rob_er, 
                                ggplot2::guide_colorbar(title = "AUC(R)")) +
  ggplot2::annotate(x = 15, y = .5, geom = "point", col = "black", size = 4) +
  ggplot2::scale_x_continuous(breaks = c(0, 7, 15, 22, 30), 
                              labels = c(1/8, 1/4, 1, 4, 8)) +
  ggplot2::theme_minimal()
#ggsave(filename = "robust_topology_heatmap.png")
```
